A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-15 paper/paper.tex
Minor edits

\section{Extensions}\label{sec:extensions}
\paragraph{Vertex labels and loops} If vertices are labelled, replace ${\langle
V(G),V(H) \rangle}$ in \lineref{FirstExpandCall} with a set of label classes, one for each label that appears in both $\V(G)$ and
$\V(H)$. If vertex labels are represented as positive integers, represent loops
as negative integers.

\paragraph{Directed graphs without edge labels} Let $A_G$ and $A_H$ be
adjacency matrices of $G$ and $H$. For each vertex pair $(t,u)$ in graph $G$ or
$H$, the adjacency matrix entry takes the value 0 if the vertices are not
adjacent, 1 if the two vertices share a single edge in the direction $t
\rightarrow u$, 2 if they share a single edge in the direction $u \rightarrow
t$, and 3 if there are edges in both directions. Where
\linerangeref{NewPWithEdge}{InnerLoopEnd} of the basic algorithm split the
label class $\langle P',T' \rangle$ according to whether vertices are adjacent
to $v$ (resp. $w$), we now perform a four-way split where each vertex is
classified according to the label on its adjacency matrix from $v$ (resp. $w$).
This is shown in Algorithm~\ref{labDirAlg}, where $L=\{0,1,2,3\}$.

@@

\paragraph{Maximum Common \emph{Connected} Subgraph} 
The common subgraph must be connected. We consider only undirected graphs. 
Modify \McSplit\ by permitting branching only on a vertex $v$ that has at
least one non-zero element in its bit-string label.

@@

? MENTION PROGRAMMING LANGUAGES, COMPILER FLAGS, MCSa1 ALGORITHM

%Parallel experiments used 32 threads per machine,
%using all 16 physical cores with hyper-threading enabled.
All experiments used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which the number of distinct vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph.

>>>>

\section{Extensions}\label{sec:extensions}

\paragraph{Vertex labels and loops} If vertices are labelled, replace ${\langle
V(G),V(H) \rangle}$ in \lineref{FirstExpandCall} with a set of label classes,
one for each label that appears on at least one vertex of both $G$ and $H$.
Loops may be treated as a label modifier: assuming the original vertex labels
are positive integers, we replace the label $l$ with $-l$ on each vertex that
has a loop.

\paragraph{Directed graphs without edge labels} Let $A_G$ and $A_H$ be
adjacency matrices of $G$ and $H$. For each vertex pair $(t,u)$ in graph $G$ or
$H$, the adjacency matrix entry takes the value 0 if the vertices are not
adjacent, 1 if the two vertices share a single edge in the direction $t
\rightarrow u$, 2 if they share a single edge in the direction $u \rightarrow
t$, and 3 if there are edges in both directions. Where
\linerangeref{NewPWithEdge}{InnerLoopEnd} of the basic algorithm split the
label class $\langle P',T' \rangle$ in two, we now perform a four-way split
where each vertex is classified according to the label on its adjacency matrix
entry from $v$ or $w$.  This is shown in Algorithm~\ref{labDirAlg}, where
$L=\{0,1,2,3\}$.

@@

\paragraph{Maximum Common \emph{Connected} Subgraph} The common subgraph must
be connected. We consider only undirected graphs.  Modify \McSplit\ by
permitting branching only on a vertex $v$ that has at least one non-zero
element in its bit-string label.  We can represent this information compactly,
and without increasing time complexity at each search node, by storing an extra
bit with each label class.  This bit takes the value $1$ if and only if the vertices in
the class are adjacent to at least one vertex in $M$.

@@

? MENTION PROGRAMMING LANGUAGES, COMPILER FLAGS, MCSa ALGORITHM AND
BITSET IMPLEMENTATION

%Parallel experiments used 32 threads per machine,
%using all 16 physical cores with hyper-threading enabled.
All ??? experiments used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which the number of distinct vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph.
